R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-03-05 README.Rmd
ranem robspack to rtorf

---
title: "robspack"
output: github_document
---

@@

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/ibarraespinosa/robspack)
[![R build
status](https://github.com/ibarraespinosa/robspack/workflows/R-CMD-check/badge.svg)](https://github.com/ibarraespinosa/robspack/actions)
[![R build
status](https://github.com/ibarraespinosa/robspack/workflows/draft-pdf/badge.svg)](https://github.com/ibarraespinosa/robspack/actions)

@@

`robspack` only depends on `data.table`, which is basically parallel C, 
so it can be installed in any machine.

@@

```{r, eval = F}
remotes::install_github("ibarraespinosa/robspack")
```

```{r, include = T, message=F, warning=F}
library(robspack)
library(data.table)
```

@@

## Application for other sectors
In this package we are sharing scripts to process other sectors
The scripts are available in the path 
`https://github.com/ibarraespinosa/robspack/tree/main/rscripts`

>>>>

---
title: "R Tools for Obspack, Footprints and Receptors (rtorf)"
output: github_document
---

@@

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/ibarraespinosa/rtorf)
[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/R-CMD-check/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)
[![R build
status](https://github.com/ibarraespinosa/rtorf/workflows/draft-pdf/badge.svg)](https://github.com/ibarraespinosa/rtorf/actions)

@@

`rtorf` only depends on `data.table`, which is basically parallel C, 
so it can be installed in any machine.

@@

```{r, eval = F}
remotes::install_github("ibarraespinosa/rtorf")
```

```{r, include = T, message=F, warning=F}
library(rtorf)
library(data.table)
```

@@

## Application for other sectors
In this package we are sharing scripts to process other sectors
The scripts are available in the path 
`https://github.com/ibarraespinosa/rtorf/tree/main/rscripts`
